---
title: "Analysis and Comparison of Multiple Regression Methods for Credit Data"
author: "Liang Hao, Andrew Shibata"
date: "11/4/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(xtable.comment = FALSE)
options(knitr.comment = FALSE)
library(glmnet)
library(pls)
```

## Introduction
These are the accompanying slides to our project which bears the same title.

In the following slides, we would introduce the data set, goal, methods, results and conclusions for the project.

## Data
The data for this project, the [Credit](http://www-bcf.usc.edu/~gareth/ISL/Credit.csv) come from the generous contribution of *An Introduction to Statistical Learning*.


|Predictor|Predictor|Response|
|-----|-----|-----|
|Quantitative|Qualitative|Quantitative|
|Income, Limit, Rating, Cards, Age, Education|Gender, Student, Married, Ethnicity|Balance|


## Goal
The goal of this project is thus to choose and fit a regression model in order to predict the *Balance* of any new client with the above information as input.

## Methods
The regression methods that we will use in this project include:

* Ordianry Linear Squares (OLS)

### Shrinkage Methods

- Ridge Regression (RR)
  
- Lasso Regression (LR)

### Dimensional Reduction Methods

- Principal Components Regression (PCR)
  
- Partial Least Squares Regression (PLSR)


## Shrinkage Methods:
### Ridge Regression
$$\sum_{i = 1}^{n}(y_{i} - \beta_{0} - \sum_{j = 1}^{p}\beta_{j}x_{ij})^{2} + \lambda \sum_{j = 1}^{p}\beta_{j}^{2} = RSS  + \lambda \sum_{j = 1}^{p}\beta_{j}^{2} $$

### Lasso Regression
$$\sum_{i = 1}^{n}(y_{i} - \beta_{0} - \sum_{j = 1}^{p}\beta_{j}x_{ij})^{2} + \lambda \sum_{j = 1}^{p}|\beta_{j}| = RSS + \lambda \sum_{j = 1}^{p}|\beta_{j}|$$


## Dimensional Reduction Methods:
### Principal Components Regression

### Partial Least Squares Regression

## Cross-validation (CV)

- Definition: Model validation technique for assessing how the results of a statistical analysis will generalize to an independent data set

- Purpose: define a dataset to "test" the model in the training phase, in order to limit problems like overfitting, give an insight on how the model will generalize to the test dataset, etc.

- Summary: combines (averages) measures of fit (prediction error) to derive a more accurate estimate of model prediction performance.


## Results
### Ridge vs. Lasso

### PCR vs. PLSR

## Conclusions
In the end, we may conclude that 

## After Thoughts
In the analysis, we also realized that ....

Therefore, in the future, 




This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

