---
title: "Analysis and Comparison of Multiple Regression Methods for Credit data set"
author: "Liang Hao, Andrew Shibata"
date: "11/2/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(xtable.comment = FALSE)
options(knitr.comment = FALSE)
library(glmnet)
library(pls)
```

## The slides
These are the accompanying slides to our project which bears the same title.

In the following slides, we would discuss 

## Data
The data for this project, the [Credit](http://www-bcf.usc.edu/~gareth/ISL/Credit.csv) come from the generous contribution of *An Introduction to Statistical Learning*.

## Goal
The goal of this project is thus to choose and fit a regression model in order to predict the *Balance* of any new client with the above information as input.

## Methods
The regression methods that we will use in this project include

* Ordianry Linear Squares (OLS)

* Shrinkage Methods

  - Ridge Regression (RR)
  
  - Lasso Regression (LR)

* Dimensional Reduction Methods

  - Pricipal Components Regression (PCR)
  
  - Partial Least Squares Regression (PLSR)

## Results
### Ridge vs. Lasso

### PCR vs. PLSR

## Conclusions
In the end, we may conclude that 

## After Thoughts
In the analysis, we also realized that ....

Therefore, in the future, 




This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

